iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-28 manuscript/main.tex
first go at specific author contributions
not filters

Importantly, the linking paradigm extends to multiple panels, whereby a panel can transmit to multiple receivers, and a receiving panel can transmit its own selection to another plot.
Chains of linked plots allow users to mimic the arbitrarily complex gating strategies often found in analyses of flow cytometry data \citep{finak2014opencyto}.
Nevertheless, iSEE augments this functionality with the advantage of integrating filters based on any feature and column metadata present in a SummarizedExperiment object.
Lastly, both tables and plot panels may be used as sources and targets of dynamically linked selections (e.g., selecting a table row to control the coloring of data points in a plot).

@@

\subsection*{Author contributions}
All authors contributed conceptually and technically to the development and maintenance of large sections of the package code.
All authors wrote and approved the final manuscript.

>>>>

Importantly, the linking paradigm extends to multiple panels, whereby a panel can transmit to multiple receivers, and a receiving panel can transmit its own selection to another plot.
Chains of linked plots allow users to mimic the arbitrarily complex gating strategies often found in analyses of flow cytometry data \citep{finak2014opencyto}.
Nevertheless, iSEE augments this functionality with the advantage of integrating selections based on any feature and column metadata present in a SummarizedExperiment object.
Lastly, both tables and plot panels may be used as sources and targets of dynamically linked selections (e.g., selecting a table row to control the coloring of data points in a plot).

@@

\subsection*{Author contributions}
All authors contributed conceptually and technically to the development and maintenance of large sections of the package code.
A.T.L.L. and F.M. developed the application and data infrastructure.
K.R.A and C.S. developed the plotting framework.
F.M. developed the code tracking and user interface.
All authors contributed to testing the application on all data sets.
All authors wrote and approved the final manuscript.
